### 2021-06-07 paper/report.tex
Update figures in report to use the new versions.

Modelling a population of agents according to actual demographic characterists means that
we can use a wide array of data to identify and estimate the model's many
parameters.\footnote{See section S.X of the supplementary materials for an
overview.}\comment[id=HM]{Need to make a list including symbols, maybe you can fetch the
parameters from the model and then we brainstorm re notation?} Mobility data is used to
model the reductions in work contacts. School and daycare policies are incorporated
directly from official directives. Infection rates by age and geographical region are
estimated to match to officially recorded numbers; so is the prevalence of virus strains.
In order to translate simulated cases in our model to officially recorded cases, we use
the model depicted in Figure~\ref{fig:model_for_official_cases}. \comment[id=HM]{Add a
sentence.} A further advantage is that the simulated data have a structure that resembles
datasets used for regression models, which allows additional plausibility checks by
re-running the same models on the model-generated data.\comment[id=HM]{Only keep if we
actually do something like that.}

@@

We apply this model to Germany. In March and April 2020, the country broke the first wave
of the pandemic fairly quickly. Between mid-May and mid-September, daily new infections
were below 20 per Million and day.\comment[id=HM]{Cite our world in data} We model the
period mid-September 2020 to the end of May 2020. We pick the starting date for two
reasons. First, we do not include the first wave because the environment was very
different (e.g., aggregate PCR test capacity was much lower and we would require a very
different model for calculating the share of known cases) and some data was not recorded
yet.\comment[id=HM]{True?}. Second, a large fraction cases during summer of 2020 were
traced to international travel,\comment[id=HM]{citation?}, but the precise number is
difficult to model.

@@

    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../figures/results/figures/scenario_comparisons/combined_fit/full_new_known_case}
        \caption{{\small Recorded cases: Empirical and simulated}}
        \label{fig:aggregated_fit}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../figures/results/figures/data/stringency2}

@@

        \caption{{\small Tests and vaccinations}}
        \label{fig:antigen_tests_vaccinations}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../figures/results/figures/data/share_of_b117_acc_to_rki}

>>>>

Modelling a population of agents according to actual demographic characteristics means
that we can use a wide array of data to identify and estimate the model's many
parameters.\footnote{See section S.X of the supplementary materials for an
overview.}\comment[id=HM]{Need to make a list including symbols, maybe you can fetch the
parameters from the model and then we brainstorm re notation?} Mobility data is used to
model the reductions in work contacts. School and daycare policies are incorporated
directly from official directives. Infection rates by age and geographical region are
estimated to match to officially recorded numbers; so is the prevalence of virus strains.
In order to translate simulated cases in our model to officially recorded cases, we use
the model depicted in Figure~\ref{fig:model_for_official_cases}. \comment[id=HM]{Add a
sentence.} A further advantage is that the simulated data have a structure that resembles
datasets used for regression models, which allows additional plausibility checks by
re-running the same models on the model-generated data.\comment[id=HM]{Only keep if we
actually do something like that.}

@@

We apply this model to Germany. In March and April 2020, the country broke the first wave
of the pandemic fairly quickly. Between mid-May and mid-September, daily new infections
were below 20 per Million and day.\comment[id=HM]{Cite our world in data} We model the
period mid-September 2020 to the end of May 2020. We pick the starting date for two
reasons. First, we do not include the first wave because the environment was very
different (e.g., aggregate PCR test capacity was much lower and we would require a very
different model for calculating the share of known cases) and some data was not recorded
yet.\comment[id=HM]{True?}\comment[id=Klara]{We would definitely need to model national
and international travel which you mention below. Regarding data I think everything would
be available. The low numbers during summer in our sample size might also be a problem
because Covid might go extinct in our model when case numbers are so low.}. Second, a
large fraction cases during summer of 2020 were traced to international
travel,\comment[id=HM]{citation?}\comment[id=Klara]{There was a comment by minister Spahn
that half of cases during the summer months were due to travel to the Baltic
(\url{https://twitter.com/krstorevic/status/1396516025181556737}) but I know of no data.
We should probably check the RKI reports of July, Aug and Sep}, but the precise number is difficult to model.

@@

    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../figures/results/figures/scenario_comparisons/combined_fit/full_new_known_case}
        \caption{{\small Recorded cases: Empirical and simulated}}
        \label{fig:aggregated_fit}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../figures/results/figures/data/stringency_with_seasonality}

@@

        \caption{{\small Tests and vaccinations}}
        \label{fig:antigen_tests_vaccinations}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../figures/results/figures/data/testing/assumed_overall_share_known_cases}
